---
title: "Suicide-Compiler"
author: "sextonjf"
date: "10/1/2021"
output: html_document
runtime: shiny
---

First, load the necessary libraries.
```{r setup}
library(shiny)
```

Then, load the appropriate data:
```{r}
suicides <- read.csv("C:\\rProjects\\suicide\\suicides2.0\\all_suicides.csv")
```

male_white_marst'), male_white_marst)
  assign(paste0(toString(year_int), 'male_black_marst'), male_black_marst)
  assign(paste0(toString(year_int), 'male_aian_marst'), male_aian_marst)
  assign(paste0(toString(year_int), 'male_asian_marst'), male_asian_marst)
  assign(paste0(toString(year_int), 'male_mixed_marst'), male_mixed_marst)
  assign(paste0(toString(year_int), 'male_pacific_marst'), male_pacific_marst)
  assign(paste0(toString(year_int), 'male_otherrace_marst'), male_otherrace_marst)
  assign(paste0(toString(year_int), 'male_hispanic_marst')


```{r}
races <- c("White", "Black", "American Indian / Alaskan Native (AIAN)",
           "Asian", "Mixed", "Pacific Islander", "Other")
sexes <- c("Male", "Female")
ethnicities <- c("Hispanic", "Non-Hispanic")

ui <- fluidPage(
  # Application title
  titlePanel("U.S. Suicide Compiler"),
  
  # Sidebar with a selection input for demographic parameters
  checkboxGroupInput("race", "Race of interest?", races),
  checkboxGroupInput("sex", "Sex of interest?", sexes),
  sliderInput("age", "Age range of interest?", value=c(1,120), min=1, max=120),
  checkboxGroupInput("ethnicity", "Ethnic status of interest?", ethnicities)
)
```


## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r eruptions, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r tabsets, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package = "shiny"),
  options = list(
    width = "100%", height = 550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



